On the presentation of orthogonal groups over polynomial rings

### 2019-06-01 dl-paper.tex
Added more text to lemma 33

\begin{lemma}
 The operators $T_\alpha$ satisfy $\text{R3}_{1,0}$.
\end{lemma}
\begin{proof}
We have to show that $[T_\alpha(aX^{-1}), T_\beta(b)](g, h, u) = (g, h, u)$ for $\beta\in Z(\alpha)$, $a, b\in A$. Suppose $p(g, h, u) \in P_\alpha(m)$ for some $m \in M$. It follows from~\cref{P0-conj-invariant} that $P_\alpha\left(\tfrac{m}{1-am}\right)$ is stable under conjugation with $x_\beta(b)$, therefore from~\cref{SR:additivity} we obtain that 
\begin{gather*}
\begin{multlined} \nonumber
  T_\beta(b) T_\alpha(aX^{-1}) T_\beta(-b) T_\alpha(-aX^{-1})(g, h, u) \sim \\
  \sim T_\beta(b) T_\alpha(aX^{-1}) \left(x_\beta(-b) x_\alpha(-aX^{-1}) \cdot g, h \cdot x_{\alpha}\left(\tfrac{aX^{-1}}{1-am}\right) \cdot h^{-1}_\alpha(1-am) \cdot р x_\beta(b), u(1-am)\right) = \\ =
  \left( [x_\beta(b), x_{\alpha}(aX^{-1}] \cdot g, h \cdot h', u] \right) \sim \left( g, h, u\right), \end{multlined} \\
\begin{multlined} \nonumber \text{ where }
 h' = x_{\alpha}\left(\tfrac{aX^{-1}}{1-am}\right) \cdot h^{-1}_\alpha(1-am) \cdot р x_\beta(b) \cdot x_{\alpha}(-a(1-am)X^{-1}) \cdot x_{\beta}(-b) = \\ = h_\alpha^{-1}(1-am) \left[x_\alpha(\tfrac{aX^{-1}}{1-am}), x_\beta(b)\right] = h_\alpha^{-1}(1-am). \qedhere \end{multlined} \end{gather*}

\end{proof}

\begin{lemma}
 For $a, b\in A$, $f, g \in M[X]$, $\alpha \neq \pm \beta \in \Phi$ holds
 \[ T_\beta(f) T_\alpha(aX^{-1})  T_\beta(g) T_\alpha(bX^{-1})(g, h, u) \]
\end{lemma}
\begin{proof}
Suppose $(g, h, u)$ is such that $p(g, h, u) \in P_\alpha(m)$ for some $m \in M$.
Set $h' := x_\alpha\left(-\tfrac{aX^{-1}}{1+am}\right) \cdot h^{-1}_\alpha(1+am) \cdot x_\alpha\left(-bX^{-1}\left(1 + \tfrac{bm}{1+am}\right)^{-1}\right) =
  x_\alpha\left(- \tfrac{(a+b)X^{-1}}{1 + (a + b)m}\right) \cdot h^{-1}_\alpha(1+am).$
The assertion for $\text{R1}_1$ is obtained via~\cref{SR:additivity}:
\begin{multline} \nonumber T_\alpha(bX^{-1}) T_\alpha(aX^{-1}) \left(g,\ h,\ u\right) \sim \\ \sim
T_\alpha(bX^{-1}) \left(x_\alpha(aX^{-1})\cdot g,\ h \cdot x_\alpha\left(-\tfrac{aX^{-1}}{1 + am}\right) \cdot h^{-1}_\alpha(1 + am),\ u(1 + am)\right) = \\
 = \left( x_\alpha\left((a+b)X^{-1}\right)\cdot g,\ h \cdot h',\ u(1 + am + bm) \right) \sim T_\alpha((a+b)X^{-1}) \left( g,\ h,\ u\right), \end{multline}

\end{proof}

>>>>

\begin{lemma}
 The operators $T_\alpha$ satisfy $\text{R3}_{1,0}$.
\end{lemma}
\begin{proof}
We have to show that $[T_\alpha(aX^{-1}), T_\beta(b)](g, h, u) = (g, h, u)$ for $\beta\in Z(\alpha)$, $a, b\in A$. Suppose $p(g, h, u) \in P_\alpha(m)$ for some $m \in M$. It follows from~\cref{P0-conj-invariant} that $P_\alpha\left(\tfrac{m}{1-am}\right)$ is stable under conjugation with $x_\beta(b)$, therefore from~\cref{SR:additivity} we obtain that 
\begin{gather*}
\begin{multlined} \nonumber
  T_\beta(b) T_\alpha(aX^{-1}) T_\beta(-b) T_\alpha(-aX^{-1})(g, h, u) \sim \\
  \sim T_\beta(b) T_\alpha(aX^{-1}) \left(x_\beta(-b) x_\alpha(-aX^{-1}) \cdot g, h \cdot x_{\alpha}\left(\tfrac{aX^{-1}}{1-am}\right) \cdot h^{-1}_\alpha(1-am) \cdot р x_\beta(b), u(1-am)\right) = \\ =
  \left( [x_\beta(b), x_{\alpha}(aX^{-1}] \cdot g, h \cdot h', u] \right) \sim \left( g, h, u\right), \end{multlined} \\
\begin{multlined} \nonumber \text{ where }
 h' = x_{\alpha}\left(\tfrac{aX^{-1}}{1-am}\right) \cdot h^{-1}_\alpha(1-am) \cdot р x_\beta(b) \cdot x_{\alpha}(-a(1-am)X^{-1}) \cdot x_{\beta}(-b) = \\
 = h_\alpha^{-1}(1-am) \left[x_\alpha(\tfrac{aX^{-1}}{1-am}), x_\beta(b)\right] = h_\alpha^{-1}(1-am). \qedhere \end{multlined} \end{gather*}
\end{proof}

\begin{lemma} For $a, b\in A$, $f_1, f_2 \in M[X]$, $\alpha \neq \pm \beta \in \Phi$ holds
 \[ T_\beta(Xf_1) T_\alpha(bX^{-1})  T_\beta(Xf_2) T_\alpha(aX^{-1})(g, h, u) = \left(g' \cdot g, h \cdot h', u(1+(a+b)m)\right), \]
where $h' = x_\alpha\left(\tfrac{(a+b)X^{-1}}{1+(a+b)m}\right)$, $g' = x_\beta(Xf_1) \cdot x_\alpha\left(bX^{-1}\right) \cdot x_\beta(Xf_2) \cdot x_\alpha\left( aX^{-1}\right)$.
 \end{lemma}
\begin{proof}
Suppose $(g, h, u)$ is such that $p(g, h, u) \in P_\alpha(m)$ for some $m \in M$.
Set $h' := x_\alpha\left(-\tfrac{aX^{-1}}{1+am}\right) \cdot h^{-1}_\alpha(1+am) \cdot x_\alpha\left(-bX^{-1}\left(1 + \tfrac{bm}{1+am}\right)^{-1}\right) =
  x_\alpha\left(- \tfrac{(a+b)X^{-1}}{1 + (a + b)m}\right) \cdot h^{-1}_\alpha(1+am).$
Notice that $x_\beta(Xf)$, $x_\beta(Xg)$ belong to $P_\alpha(0)$ therefore from~\cref{SR:additivity} we obtain that:
\begin{multline} \nonumber T_\beta(Xf_1) \cdot T_\alpha(bX^{-1}) \cdot T_\beta(Xf_2) \cdot T_\alpha(aX^{-1}) \left(g,\ h,\ u\right) \sim \\ 
\sim T_\beta(Xf_1) \cdot T_\alpha(bX^{-1}) \left(x_{\beta}(Xf_2) \cdot x_\alpha(aX^{-1})\cdot g,\ h \cdot x_\alpha\left(-\tfrac{aX^{-1}}{1 + am}\right) \cdot h^{-1}_\alpha(1 + am),\ u(1 + am)\right) \sim \\
 \sim \left( g' \cdot g,\ h \cdot x_\alpha\left(-\tfrac{(a+b)X^{-1}}{1+(a+b)m}\right),\ u(1 + am + bm) \right). \end{multline}  
\end{proof}
